---
title: "API notes"
output: html_notebook
---

```{r}
library(httr)
```

## Authentication via Personal key

Get secret key from UI
The secret key is: `n0ns3ns3l3tt3rsandnumb3rs` (and obviously fake, put yours here)

```{bash}
curl -H 'User-Agent: testApp (davidrgparr@gmail.com)' https://api.netlify.com/api/v1/sites?access_token=n0ns3ns3l3tt3rsandnumb3rs
```


## Request - response

Get sites data from API with inline personal token URL

```{r get sites simple}
GET(
  "https://api.netlify.com/api/v1/sites?access_token=n0ns3ns3l3tt3rsandnumb3rs"
) -> sites
```

```{r structure sites}
str(sites)
```

```{r content sites}
content(sites)[[1]]
```

### Create a site

```{r post simple site with list of args}
POST("https://api.netlify.com/api/v1/sites?access_token=n0ns3ns3l3tt3rsandnumb3rs",
     verbose(),
     encode="json",
     add_headers(),
     body = list(name = "satrday-mycity",
                 custom_domain = "www.mycity2018.daveparr.info")) -> new_site
```

## Include a repo support?

>You can link a repository while you create a site.
This is an example payload from such a successful site creation (POST to https://api.netlify.com/api/v1/sites).
`{"repo":{"provider":"github","id":74777123,"repo":"account_name/repository_name","private":false,"branch":"master","cmd":"jekyll build","dir":"_site/","deploy_key_id":"5a908857a6188f724c466bed"}}`
Note that there are two ID's there - a github repo ID (which you can get from their API), and a deploy key which you'll need to setup via our API before you'll be able to create a usable repo object.  
The call to achieve this is a POST to https://api.netlify.com/api/v1/deploy_keys.  This call responds with JSON containing "public_key" and "id" parameters (you'll need to put public_key in place at github), and keep "id" for the repo definition I already quoted.
Some more details on using our API:
The best ways to get familiar with our API are NOT currently in our documentation.
https://open-api.netlify.com has a fairly thorough list of the available calls but is not entirely fleshed out or complete as it has to be manually updated with new calls.  So...
checking how our UI actually uses the API in your browser dev tools will be the best guide to using every feature you can control with the API.  I realize this is a bit inelegant but it is definitely the best way to figure out what structure a Repo object has or what the normal "order of operations" is in creating a site.


```{r post deploy key}
POST(
  "https://api.netlify.com/api/v1/deploy_keys?access_token=n0ns3ns3l3tt3rsandnumb3rs",
  verbose()
  ) -> deploy_key
content(deploy_key)
content(deploy_key)$id ->  netlify_deploy_key_id
netlify_deploy_key_id
```

```{r get repo id}
GET("https://api.github.com/repos/DaveParr/simpletest") -> github_repo

content(github_repo)$id -> github_repo_id
github_repo_id
```


```{r create site with repo}
POST(
  "https://api.netlify.com/api/v1/sites?access_token=n0ns3ns3l3tt3rsandnumb3rs",
  verbose(data_in = TRUE),
  body = '{"repo":{"provider":"github","id":147546519,"repo":"DaveParr/simpletest","private":false,"branch":"master","cmd":"hugo","dir":"public","deploy_key_id":"putdeploykeyhere"}}',
  encode = 'json'
  ) -> new_site
```

Creates new site, but no deploy

Postman succeeded with deploying with exact same argument, but only with body set to json. Build failed though, git refs/heads/master does not exist

Also tried this in postman:
```{json}
{
  "build_settings":{
    "public_repo":true
  }, 
  "repo":{
    "id":147546519, 
    "provider":"github", 
    "deploy_key_id":"putdeploykeyhere", 
    "repo_path":"DaveParr/simpletest", 
    "repo_branch":"master", "dir":"public", 
    "cmd":"hugo --minify", 
    "public_repo":true, 
    "branch":"master", 
    "repo_url":"https://github.com/DaveParr/simpletest", 
    "env":{
      "HUGO_VERSION":"0.48", "HUGO_ENV":"production", "HUGO_ENABLEGITINFO":"true"
    }
  }
}
```

Triggered netlify to _try_ to deploy, but failed on accessing repo

```
5:24:27 PM: Build ready to start
5:24:28 PM: build-image version: 42bca793ccd33055023c56c4ca8510463a56d317
5:24:28 PM: buildbot version: 6bab8b64bbd90091082af19fedf16bf73d502e5e
5:24:28 PM: Fetching cached dependencies
5:24:28 PM: Failed to fetch cache, continuing with build
5:24:28 PM: Starting to prepare the repo for build
5:24:29 PM: git ref refs/heads/master does not exist or you do not have permission
5:24:29 PM: Failing build: Failed to prepare repo
5:24:29 PM: failed during stage 'preparing repo': git ref refs/heads/master does not exist
5:24:29 PM: Finished processing build request in 911.325328ms
```
